The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-10 rational.tex
more on functions

\paragraph*{Non-termination.}
As is well known in category theory, Compact Closed Categories contain
trace operations.  In the context of {{langRev}} this implies that
{{eta+}}/{{eps+}} allow the construction of a {{trace+}} operator
(detailed in Section \ref{sec:monoidal-constructions}) hence
introducing \emph{non-termination} into the language
\cite{infeffects}.

@@

Let us use the shorthand {{b1 -o b2 = -b1 + b2}}

\roshan{Also: additive functions aren't values - they are
  possibilities. Multiplicative functions really are values.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions in {{langRevEE}} specific to Addition and Multiplication}
\label{sec:neg-constructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conventional Higher Order Functions}

>>>>

\paragraph*{Non-termination.}
As is well known in category theory, Compact Closed Categories contain
trace operations.  In the context of {{langRev}} this implies that
{{eta+}}/{{eps+}} allow the construction of a {{trace+}} operator
(detailed in Section \ref{sec:monoidal-constructions}) hence
introducing \emph{non-termination} into the language (in the presence
of recursive types) \cite{infeffects}.

@@

Let us use the shorthand {{b1 -o+ b2 = 0 <-> -b1 + b2}}. See
Sec. \ref{sec:hof} for a discussion of the additive functions
vs. multiplicative functions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions specific to Negatives and Fractions}
\label{sec:specific-constructions}

While the constructions in Sec \ref{sec:monoidal-constructions} apply
to both the {{(0,+)}} and {{(1,*)}} monoids, each construction
presented here applies to a specific monoid.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conventional Higher Order Functions}
\label{sec:hof}
